Light inextensible strings under tension in the Schwarzschild geometry

### 2019-08-28 string_physics_teacher.tex
another insight

\noindent which would give~$R$ as a function of~$\left(r,r'\right)$.
Considering~$r'(\phi)=0$ shows that if a string is tangential at a
point with~$r_0>2M$, then it obeys, to first order, $r''=r-2M$, while
tangential null geodesics follow $r''=r-3M$.  This shows that a taut
string would {\em look} curved to a local observer, having a (visual)
radius of curvature of $r_0^2/M\sqrt{1-2M/r_0}$ (the extra term comes
from the fact that appearance is driven by local $ds$, not
Schwarzschild $r$).  At the photon sphere $r_0=3M$, such a string
would appear to have a radius of~$\sqrt{27}M$.  For a solar mass black
hole this would be about $15\unit{km}$, a readily understandable
result.

>>>>

\noindent which would give~$R$ as a function of~$\left(r,r'\right)$.
Considering~$r'(\phi)=0$ shows that a tangential string at a point
with~$r_0>2M$ obeys, to first order, $r''=r-2M$, while tangential null
geodesics follow $r''=r-3M$.  This shows that a taut string would {\em
  look} curved to a local observer, having a (visual) radius of
curvature of $r_0^2/M\sqrt{1-2M/r_0}$ (the extra term comes from the
fact that appearance is driven by local $ds$, not Schwarzschild $r$).
At the photon sphere $r_0=3M$, such a string would appear to have a
radius of~$\sqrt{27}M$.  For a solar mass black hole this would be
about $15\unit{km}$, a readily understandable result.
